Laves polyhedra in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and its lattice dynamics

### 2021-01-26 paper_tennantite.tex

At fitting, ADPs are considered as a combination of quantum zero vibrations, thermal vibrations, and static shifts\cite{Trueblood1996,Bentien2005,Nakatsuka2011}.
The thermal expansion of the crystal, and the corresponding change of the atomic vibration frequencies depend on the temperature, and may be described using a quasi-harmonic approximation\cite{willis1975thermal,Bentien2005}.
As a result ADP, is described by u\textsubscript{calc}=xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
The result of tennantite ADPs fitting is presented in the Fig.~\ref{fig:enst_temp}, and Table~\ref{tab:enst_temp}.
The average oscillation frequency of the selected atom, and its characteristic Einstein temperature, T\textsubscript{E}, can be obtained  assuming x~$=$~1.
The maximal oscillation frequency of the selected atom and its characteristic Debye temperature, T\textsubscript{D}, corresponds to the case x~$=$~0.
Distributions of zero-point oscillations, u\textsubscript{$0E$} or u\textsubscript{$0D$}, were obtained applying T~$=$~0 in the Einstein or Debye formulas.
Thus, the contribution of Einstein or Debye parts to atomic displacements consists of zero quantum vibrations, u\textsubscript{$0E$} or u\textsubscript{$0D$}, and a temperature-dependent part, u\textsubscript{E}(T) or u\textsubscript{D}(T), which can be associated with the thermal motion of atoms.
That is, u\textsubscript{E} = u\textsubscript{$0E$} + u\textsubscript{E}(T), and u\textsubscript{D} = u\textsubscript{$0D$} + u\textsubscript{D}(T). The shift of an atom from its equilibrium position due to any reason other than thermal vibrations is the sum of zero vibrations and static shift: u\textsubscript{shift} = u\textsubscript{$0E$} + u\textsubscript{static} or u\textsubscript{shift} = u\textsubscript{$0D$} + u\textsubscript{static}\cite{Dudka2019}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{ADP_aproximation_eng}% Here is how to import EPS art
\caption{\label{fig:enst_temp} Equivalent parameters U\textsubscript{eq} of the mean-square displacements of atoms in tennantite. Points are the experimental data. The solid curves show the fit of the temperature dependences according to the expanded Einstein model.}
\end{figure}

@@

\begin{table}
\caption{\label{tab:enst_temp}
Einstein temperatures, dispersions of zero-point oscillations u\textsubscript{$E_{0}$} u\textsubscript{static}, and u\textsubscript{shift} for atoms in tennantite. $R=\sum |u\textsubscript{eq} - u\textsubscript{calc} |/\sum u\textsubscript{eq}$ is the residual factor of the LS procedure.
}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{cccccc}

>>>>

At fitting, ADPs are considered as a combination of quantum zero vibrations, thermal vibrations, and static shifts\cite{Trueblood1996,Bentien2005,Nakatsuka2011}.
The thermal expansion of the crystal, and the corresponding change of the atomic vibration frequencies depend on the temperature, and may be described using a quasi-harmonic approximation\cite{willis1975thermal,Bentien2005}.
As a result ADP, is described by u\textsubscript{calc}~$=$~xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
The result of tennantite ADPs fitting is presented in the Fig.~\ref{fig:enst_temp}, and Table~\ref{tab:enst_temp}.
The average oscillation frequency of the selected atom, and its characteristic Einstein temperature, T\textsubscript{E}, can be obtained  assuming x~$=$~1.
The maximal oscillation frequency of the selected atom and its characteristic Debye temperature, T\textsubscript{D}, corresponds to the case x~$=$~0.
Distributions of zero-point oscillations, u\textsubscript{0E} or u\textsubscript{0D}, were obtained applying T~$=$~0 in the Einstein or Debye formulas.
Thus, the contribution of Einstein or Debye parts to atomic displacements consists of zero quantum vibrations, u\textsubscript{0E} or u\textsubscript{0D}, and a temperature-dependent part, u\textsubscript{E}(T) or u\textsubscript{D}(T), which can be associated with the thermal motion of atoms.
That is, u\textsubscript{E} = u\textsubscript{0E} + u\textsubscript{E}(T), and u\textsubscript{D} = u\textsubscript{0D} + u\textsubscript{D}(T). The shift of an atom from its equilibrium position due to any reason other than thermal vibrations is the sum of zero vibrations and static shift: u\textsubscript{shift} = u\textsubscript{0E} + u\textsubscript{static} or u\textsubscript{shift} = u\textsubscript{0D} + u\textsubscript{static}\cite{Dudka2019}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{ADP_aproximation_eng}% Here is how to import EPS art
\caption{\label{fig:enst_temp} Equivalent parameters u\textsubscript{eq} of the mean-square displacements of atoms in tennantite. Points are the experimental data. The solid curves show the fit of the temperature dependences according to the expanded Einstein model.}
\end{figure}

@@

\begin{table}
\caption{\label{tab:enst_temp}
Einstein temperatures, dispersions of zero-point oscillations u\textsubscript{E$_{0}$} u\textsubscript{static}, and u\textsubscript{shift} for atoms in tennantite. $R=\sum |u\textsubscript{eq} - u\textsubscript{calc} |/\sum u\textsubscript{eq}$ is the residual factor of the LS procedure.
}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{cccccc}
